My title

### 2024-04-20 paper/paper.qmd
udpates to tables

@tbl-starttoendNKE shows a 
```{r}
#| label: tbl-starttoendNKE
#| tbl-cap: Changes in Starbucks Stock Price from One Week Before Legal Action Against Workers United to March 28th
#| echo: false

@@

```
@tbl-starttoendPRKS shows that there was a significant decrease in 
```{r}
#| label: tbl-starttoendPRKS
#| tbl-cap: Changes in United Parks & Recreation Stock Price from One Week Before Blackfish was Released to their Announcement that they will end their Orca Breeding Program
#| echo: false

@@

/newpage

>>>>

@tbl-starttoendNKE shows a 
```{r}
#| label: tbl-starttoendNKE
#| tbl-cap: Changes in Starbucks Stock Price from One Week Before Legal Action Against Workers United, the the Day it was Announced, to March 28th
#| echo: false

@@

kable(starttoend_NKE, 
      col.names = c("Date", 
                    "Closing Stock Price",
                    "Difference Between Stock Prices"),
      booktabs = TRUE,
      linesep = ""
)
```
@tbl-starttoendPRKS shows that there was a significant decrease in 
```{r}
#| label: tbl-starttoendPRKS
#| tbl-cap: Changes in United Parks & Recreation Stock Price from One Week Before Blackfish was Released, to the Date it was Released, to their Announcement that they will end their Orca Breeding Program
#| echo: false

@@

kable(starttoendPRKS, 
      col.names = c("Date", 
                    "Closing Stock Price",
                    "Difference Between Stock Prices"),
      booktabs = TRUE,
      linesep = ""
)
```

@tbl-starttoendSBUX shows a 
```{r}
#| label: tbl-starttoendSBUX
#| tbl-cap: Changes in Starbucks Stock Price from One Week Before Legal Action Against Workers United, the the Day it was Announced, to March 28th
#| echo: false

starttoendSBUX <- cleaned_data_SBUX |>
  filter(Date == '1991-07-12' | Date == '1991-07-18' | Date == '1998-05-19')

starttoendSBUX <-
  starttoendSBUX |> 
  mutate(Difference = Close - lag(Close))

kable(starttoendSBUX, 
      col.names = c("Date", 
                    "Closing Stock Price",
                    "Difference Between Stock Prices"),
      booktabs = TRUE,
      linesep = ""
)
```
